### 2023-12-11 README.Rmd
update readme

You can download the compendium as a zip from from this URL:
[master.zip](/archive/refs/heads/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `renv::restore` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- to re-run the code that performs the data analysis and creates the visualisations, look in the `scripts` folder and run the R and Rev script files in order. The file names contain numbers that indicate the correct order. You will need to install [RevBayes](https://revbayes.github.io/) to run some of these files. 
- finally, open `analysis/paper/paper.qmd` and render to produce the `paper.docx`, or run `quarto::quarto_render("analysis/paper/paper.qmd")` in the R console. Note that this file does not run any analysis code, it only combines the previously generated figures with the text of the manuscript.

>>>>

You can download the compendium as a zip from from this URL:
[master.zip](/archive/refs/heads/master.zip). After unzipping:
- open the `.Rproj` file in RStudio.   
- run `renv::restore` to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file).    
- to re-run the code that performs the data analysis and creates the visualisations, look in the `scripts` folder and run the R and Rev script files in order. The file names contain numbers that indicate the correct order (eg. 001, 002, etc.). You will need to install [RevBayes](https://revbayes.github.io/) to run some of these files.    
- The data analysis took about 10 hours on my Macbook Pro 2.3 GHz Core i7 with 16 Gb RAM. The full output files were too large to commit to GitHub, and so are stored on [OSF](https://osf.io/rbqa5/). If you want to skip running the entire analysis, especially the time-consuming MCMC runs, you can find the analysis output at https://osf.io/rbqa5/ in a folder called `revbayes-output`, and use that to run some of the later steps 
- finally, open `analysis/paper/paper.qmd` and render to produce the `paper.docx`, or run `quarto::quarto_render("analysis/paper/paper.qmd")` in the R console. Note that this file does not run any analysis code, it only combines the previously generated figures with the text of the manuscript to generate the manuscript.
